---
title: "Biogeoclimatic Ecosystem Classification"
output:
  html_document:
    code_folding: hide
    css: veg_report.css
    
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
require(ggplot2)
require(RColorBrewer)
require(kableExtra)
require(data.table)
library(stringr)
library(ggraph)
library(igraph)
library(tidyverse)
library(rgdal)
library(broom)
library(ggplot2)
library("rjson")
library("readxl")

```


```{r, echo=FALSE}
level_name <- "Order"
level_value <- "ORDER Poputre"
```

```{r}
ENV_Plot_data_for_level <- read.csv(file=file.path("../level", level_name, level_value,"ENV_Plot_data_for_level.csv"))

```

### Site Units
```{r choose site unit, echo=FALSE}
hier_summary <- readRDS(file.path("../level", level_name, level_value, "heir_summary_ORDER_Poputre.RDS"))
site_units <- hier_summary$SiteUnits
print(site_units)
```

### Plot Numbers with Site Units
```{r, echo=FALSE}
site_unit <- site_units[[2]]

SUTab <- fread("../BEC_ReportR/Classification_tables/ALLBECSU_2021_SU.csv")

plot_numbers_with_site_unit <- SUTab$PlotNumber[SUTab$SiteUnit == site_unit]
print(plot_numbers_with_site_unit)

```
<div class="header">
  <span class="emphasized">`r level_name` `r level_value` </span>
  <span class="emphasized">`r site_unit` </span>
</div>



```{r, echo=FALSE}
reports_dir <- "veg_reports"
csv_file_path <- function(layer_name) file.path(reports_dir, paste(layer_name, ".csv", sep="_"))


df_herb <- read.csv(file = file.path('../level', level_name, level_value, "veg_reports", "Herb_Layer.csv"))
df_moss <- read.csv(file = file.path('../level', level_name, level_value, "veg_reports", "Moss_Layer.csv"))
df_shrub <- read.csv(file = file.path('../level', level_name, level_value,"veg_reports",  "Shrub_Layer.csv"))
df_tree <- read.csv(file = file.path('../level', level_name, level_value, "veg_reports", "Tree_Layer.csv"))

len_herb <- nrow(df_herb)
len_moss <- nrow(df_moss)
len_shrub <- nrow(df_shrub)
len_tree <- nrow(df_tree)

```

```{r Join data, echo=FALSE}
df <- rbind(df_tree, df_shrub, df_herb, df_moss)
```


```{r Veg report, echo=FALSE}
df <- df[, c("Layer","ScientificName", "constantcy","meanCover","EnglishName")]

kbl(df, col.names = c("Layer", "Scientific Name", "Constantcy", "Mean Cover", "English Name"), format = "html", table.attr = "style='width:100%;'", align = "lllll") %>%
  kable_styling() %>%
  row_spec(0, extra_css = "border-bottom: 1px solid") %>%
  row_spec(len_tree, extra_css = "border-bottom: 1px solid") %>%
  row_spec(len_tree + len_shrub, extra_css = "border-bottom: 1px solid") %>%
  row_spec(len_tree + len_shrub + len_herb, extra_css = "border-bottom: 1px solid")
```
# Edatopic Grid

```{r Get soil moisture regime, echo=FALSE}
env_summary <- fromJSON(file=file.path("../level", level_name, level_value, "summaries", "env", paste(str_replace_all(level_value, " ", "_"), ".JSON",  sep="")))

soil_moisture_regime <- env_summary$MoistureRegime
soil_moisture_regime_values <- as.numeric(names(soil_moisture_regime$summary))

soil_moisture_regime_values <- soil_moisture_regime_values[!is.na(soil_moisture_regime_values)]

y_range <- range(soil_moisture_regime_values)

y_1 <- y_range[1]
y_2 <- y_range[2]

```
```{r Get aSMR data, echo=FALSE}
  
aSMR_Plot_data_for_level <- read.csv(file=file.path("../level", level_name, level_value,"aSMR_Plot_data_for_level.csv"))
asmr <- aSMR_Plot_data_for_level$aSMR
asmr <- asmr[!is.na(asmr)]
x_range <- range(asmr)

x_1 <- x_range[1]
x_2 <- x_range[2]
```


```{r, echo=FALSE}
library("ggplot2")

df=data.frame(x1=c(x_1), x2=c(x_2), y1=c(y_1), y2=c(y_2), colour=c('green'), r=c(1))
x_lab = c("v.           \npoor            ", "poor            ", "medium            ", "rich            ", "v.            \nrich            ")
y_lab = c("very wet", "wet", "very moist", "moist", "fresh", "slightly dry", "moderely dry", "very dry", "extremely dry", "excessively dry")

edatopic <- ggplot() + 
scale_x_continuous(name="Soil Nutrient Regime", labels=x_lab, limits=c(0,5), breaks=c(1,2,3,4,5), expand = c(0, 0), position = "top") + 
scale_y_continuous(name="actual Soil Moisture Regime", labels=y_lab, limits=c(0,10), breaks=c(1,2,3,4,5,6,7,8,9,10), expand=c(0, 0)) +
coord_fixed() +
geom_rect(data=df, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill=df$colour, color="black", alpha=0.5) +
geom_text(data=df, aes(x=x1+(x2-x1)/2, y=y1+(y2-y1)/2, label=r), size=4) + 
theme(
  panel.grid.major = element_line(linetype = 2, color="#A7A7A7", size = 0.3),
  panel.grid.minor.x = element_blank(),
  panel.grid.minor.y = element_blank(),
  panel.border = element_rect(colour = "black", size=1, fill=NA),
  panel.background = element_rect(fill="#F2F2F2"),
  axis.ticks.x = element_blank(),
  axis.ticks.y = element_blank(),
  axis.ticks = element_blank(),
  axis.text.x = element_text(face="bold", size=10),
  axis.text.y = element_text(face="bold", size=10, vjust=2.75),
  axis.title = element_text(face="bold") 
 )

ggsave("edatpic.png")
```

```{r, echo=FALSE}

level_names <- c("Classes", "Orders", "SubOrder", "Alliannces", "Associations")
level_labels <- unlist(c(hier_summary$Classes, hier_summary$Orders, hier_summary$SubOrder, hier_summary$Alliances, hier_summary$Associations)) 
level_labels <- level_labels[!is.na(level_labels)]

d1 <- data.frame(from=hier_summary$Classes, to=hier_summary$Orders)
d2 <- data.frame(from=d1$to, to=hier_summary$SubOrder)
d3 <- data.frame(from=d2$to, to=hier_summary$Alliances)
d4 <- data.frame(from=d3$to, to=hier_summary$Associations)
edges <- drop_na(rbind(d1, d2, d3, d4))

 
# Create a graph object 
mygraph <- graph_from_data_frame( edges )
 
# Basic tree
heigharchy <- ggraph(mygraph, layout = 'dendrogram', circular = FALSE) + 
  geom_edge_diagonal() +
  geom_node_point() +
  geom_node_label(aes(label = level_labels), repel = TRUE) +
  theme_void()

ggsave("hierarchy.png")
```

# Map

```{r, echo=FALSE}
my_spdf <- readOGR(dsn= paste0("../BEC_ReportR/Spatial_files"), verbose=FALSE)
```

```{r}
lat <- ENV_Plot_data_for_level$Latitude
lon <- ENV_Plot_data_for_level$Longitude*(-1)
lon_lat <- as.data.frame(cbind(lon,lat)) %>% drop_na()
```


```{r, echo=FALSE}
spdf_fortified <- tidy(my_spdf)

# Plot it
# library(ggplot2)
# ggplot() +
#   geom_polygon(data = spdf_fortified, aes( x = long, y = lat, group = group), fill="#69b3a2", color="white") +
#   geom_point(data=lon_lat, aes(lon, lat), alpha = 0.5, size = 1) +
#   theme_void() 


library("rnaturalearth")
library("rnaturalearthdata")
library(ggplot2)


world <- ne_countries(scale = "medium", returnclass = "sf")
bc_map <- ggplot() +
  geom_polygon(data = spdf_fortified, aes( x = long, y = lat, group = group), fill="#69b3a2", color="white") +
  geom_point(data = lon_lat, aes(x = lon, y = lat), size = 4, shape = 23, fill = "darkred") + 
  theme_void() 

ggsave("bc_map.png")

```


## Strata cover

```{r, echo=FALSE}
# strata_cover_tree <- env_summary$StrataCoverTree
# strata_cover_hurb <- env_summary$StrataCoverTree

strata_cover_tree <- ENV_Plot_data_for_level$StrataCoverTree
#asmr <- asmr[!is.na(asmr)]

```

```{r, echo=FALSE}
Tree=ENV_Plot_data_for_level$StrataCoverTree
Herb=ENV_Plot_data_for_level$StrataCoverHerb
Shrub=ENV_Plot_data_for_level$StrataCoverShrub
Moss=ENV_Plot_data_for_level$StrataCoverMoss
```

```{r, echo=FALSE}
strata_cover <- melt(data.frame(Tree, Herb, Shrub))

# Multiple plots same axis
# p <- ggplot(strata_cover, aes(factor(variable), value)) +
#   geom_violin() +
#   geom_boxplot(width = .1) 

tree <- ggplot(ENV_Plot_data_for_level, aes(StrataCoverTree, "Tree")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

herb <- ggplot(ENV_Plot_data_for_level, aes(StrataCoverHerb, "Herb")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

shrub <- ggplot(ENV_Plot_data_for_level, aes(StrataCoverShrub, "Shrub")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

moss <- ggplot(ENV_Plot_data_for_level, aes(StrataCoverMoss, "Moss")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

tree
ggsave("tree.png")

herb
ggsave("herb.png")

shrub
ggsave("shrub.png")

moss
ggsave("moss.png")

```


## Life Forms

```{r, echo=FALSE}
MasterSpeciesList <- read_excel("../BEC_ReportR/LookUp_tables/MasterSpeciesList.xlsx") 
Veg_Plot_data_for_level <- read.csv(file=file.path("../level", level_name, level_value,"Veg_Plot_data_for_level.csv"))
Veg_Plot_data_for_level$SummedCover <- Veg_Plot_data_for_level$TotalA + Veg_Plot_data_for_level$TotalB + Veg_Plot_data_for_level$Cover6 + Veg_Plot_data_for_level$Cover7

```

```{r, echo=FALSE}
df_lifeforms <- merge(x=Veg_Plot_data_for_level, y=MasterSpeciesList, by.x="Species", by.y="Code") 

```

```{r}
lifeform_0 <- df_lifeforms %>% filter(Lifeform == 0)
lifeform_1 <- df_lifeforms %>% filter(Lifeform == 1)
lifeform_2 <- df_lifeforms %>% filter(Lifeform == 2)
lifeform_3 <- df_lifeforms %>% filter(Lifeform == 3)
lifeform_4 <- df_lifeforms %>% filter(Lifeform == 4)
lifeform_5 <- df_lifeforms %>% filter(Lifeform == 5)
lifeform_6 <- df_lifeforms %>% filter(Lifeform == 6)
lifeform_7 <- df_lifeforms %>% filter(Lifeform == 7)
lifeform_8 <- df_lifeforms %>% filter(Lifeform == 8)
lifeform_9 <- df_lifeforms %>% filter(Lifeform == 9)
lifeform_10 <- df_lifeforms %>% filter(Lifeform == 10)
lifeform_11 <- df_lifeforms %>% filter(Lifeform == 11)
lifeform_12 <- df_lifeforms %>% filter(Lifeform == 12)
lifeform_13 <- df_lifeforms %>% filter(Lifeform == 13)
lifeform_14 <- df_lifeforms %>% filter(Lifeform == 14)

```

```{r}
life_form_0 <- data.frame(lifeForm0 = (lifeform_0$TotalA + lifeform_0$TotalB + lifeform_0$Cover6 + lifeform_0$Cover7))
life_form_1 <- data.frame(lifeForm1 = (lifeform_1$TotalA + lifeform_1$TotalB + lifeform_1$Cover6 + lifeform_1$Cover7))
life_form_2 <- data.frame(lifeForm2 =  (lifeform_2$TotalA + lifeform_2$TotalB + lifeform_2$Cover6 + lifeform_2$Cover7))
life_form_3 <- data.frame(lifeForm3 = (lifeform_3$TotalA + lifeform_3$TotalB + lifeform_3$Cover6 + lifeform_3$Cover7))
life_form_4 <- data.frame(lifeForm4 = (lifeform_4$TotalA + lifeform_4$TotalB + lifeform_4$Cover6 + lifeform_4$Cover7))
life_form_5 <- data.frame(lifeForm5 = (lifeform_5$TotalA + lifeform_5$TotalB + lifeform_5$Cover6 + lifeform_5$Cover7))
life_form_6 <- data.frame(lifeForm6 = (lifeform_6$TotalA + lifeform_6$TotalB + lifeform_6$Cover6 + lifeform_6$Cover7))
life_form_7 <- data.frame(lifeForm7 = (lifeform_7$TotalA + lifeform_7$TotalB + lifeform_7$Cover6 + lifeform_7$Cover7))
life_form_8 <- data.frame(lifeForm8 = (lifeform_8$TotalA + lifeform_8$TotalB + lifeform_8$Cover6 + lifeform_8$Cover7))
life_form_9 <- data.frame(lifeForm9 = (lifeform_9$TotalA + lifeform_9$TotalB + lifeform_9$Cover6 + lifeform_9$Cover7))
life_form_10 <- data.frame(lifeForm10 = (lifeform_10$TotalA + lifeform_10$TotalB + lifeform_10$Cover6 + lifeform_10$Cover7))
life_form_11 <- data.frame(lifeForm11 = (lifeform_11$TotalA + lifeform_11$TotalB + lifeform_11$Cover6 + lifeform_11$Cover7))
life_form_12 <- data.frame(lifeForm12 = (lifeform_12$TotalA + lifeform_12$TotalB + lifeform_12$Cover6 + lifeform_12$Cover7))
life_form_13 <- data.frame(lifeForm13 = (lifeform_13$TotalA + lifeform_13$TotalB + lifeform_13$Cover6 + lifeform_13$Cover7))
life_form_14 <- data.frame(lifeForm14 = (lifeform_14$TotalA + lifeform_14$TotalB + lifeform_14$Cover6 + lifeform_14$Cover7))

```


```{r}
life_form_0_plot <- ggplot(life_form_0, aes(lifeForm0, "lifeForm0")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

life_form_1_plot <- ggplot(life_form_1, aes(lifeForm1, "lifeForm1")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

life_form_2_plot <- ggplot(life_form_2, aes(lifeForm2, "lifeForm2")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

life_form_3_plot <- ggplot(life_form_3, aes(lifeForm3, "lifeForm3")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

life_form_4_plot <- ggplot(life_form_4, aes(lifeForm4, "lifeForm4")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

life_form_5_plot <- ggplot(life_form_5, aes(lifeForm5, "lifeForm5")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

life_form_6_plot <- ggplot(life_form_6, aes(lifeForm6, "lifeForm6")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

life_form_7_plot <- ggplot(life_form_7, aes(lifeForm7, "lifeForm7")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

life_form_8_plot <- ggplot(life_form_8, aes(lifeForm8, "lifeForm8")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()


life_form_9_plot <- ggplot(life_form_9, aes(lifeForm9, "lifeForm9")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

life_form_10_plot <- ggplot(life_form_10, aes(lifeForm10, "lifeForm10")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

life_form_11_plot <- ggplot(life_form_11, aes(lifeForm11, "lifeForm11")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

life_form_12_plot <- ggplot(life_form_12, aes(lifeForm12, "lifeForm12")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

life_form_13_plot <- ggplot(life_form_13, aes(lifeForm13, "lifeForm13")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

life_form_14_plot <- ggplot(life_form_14, aes(lifeForm14, "lifeForm14")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()
```

```{r}
if(count(lifeform_8) != 0) {

life_form_0_plot
ggsave(file="life_form_0_plot.png")
}
```

```{r}
if(count(lifeform_8) != 0) {

life_form_1_plot
ggsave(file="life_form_1_plot.png")
}
```

```{r}
if(count(lifeform_8) != 0) {

life_form_2_plot
ggsave(file="life_form_2_plot.png")
}
```

```{r}
if(count(lifeform_8) != 0) {

life_form_3_plot
ggsave(file="life_form_3_plot.png")
}
```

```{r}
if(count(lifeform_4) != 0) {

life_form_4_plot
ggsave(file="life_form_4_plot.png")
}
```

```{r}
if(count(lifeform_5) != 0) {


life_form_5_plot
ggsave(file="life_form_5_plot.png")
}
```

```{r}
if(count(lifeform_6) != 0) {

  life_form_6_plot
  ggsave(file="life_form_6_plot.png")
}
```

```{r}
if(count(lifeform_8) != 0) {
  life_form_7_plot
  ggsave(file="life_form_7_plot.png")
}
```

```{r}
if(count(lifeform_8) != 0) {
  life_form_8_plot
  ggsave(file="life_form_8_plot.png")
}

```

```{r}
if(count(lifeform_8) != 0) {

life_form_9_plot
ggsave(file="life_form_9_plot.png")
}
```

```{r}
if(count(lifeform_8) != 0) {

  print("RAN")
life_form_10_plot
ggsave(file="life_form_10_plot.png")
}
```

```{r}
if(count(lifeform_8) != 0) {

life_form_11_plot
ggsave(file="life_form_11_plot.png")
}
```

```{r}
if(count(lifeform_8) != 0) {

life_form_12_plot
ggsave(file="life_form_12_plot.png")
}
```

```{r}
if(count(lifeform_8) != 0) {

life_form_13_plot
ggsave(file="life_form_13_plot.png")
}
```

```{r}
if(count(lifeform_8) != 0) {

life_form_14_plot
ggsave(file="life_form_14_plot.png")
}
```


### Elevation
```{r}
life_form_0_plot <- ggplot(ENV_Plot_data_for_level, aes(Elevation, "Elevation")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

elevation
ggsave(file="elevation.png")
```


```{r}

# Life form = sum of total A, total B, cover6, cover 7
# Plot number, Species Code, Life form, Summed Cover. Then summarize by lifeform, by plot number


# Need more information about life forms plots 

# p <- ggplot(df_lifeforms, aes(factor(Lifeform), mpg)) +
#   geom_violin() +
#   geom_boxplot(width = .1)
# p
```

## BGCS Counts
```{r Counts of GIS_BGC for level, echo=FALSE}
Admin_Plot_data_for_level <- read.csv(file=file.path("../level", level_name, level_value,"Admin_Plot_data_for_level.csv"))
GIS_BGC <- Admin_Plot_data_for_level$GIS_BGC
counts_GIS_BGC <- table(GIS_BGC)
print(counts_GIS_BGC)

```
## Temperature, Precipitation, Derived
```{r, echo=FALSE}
Climate_Plot_data_for_level <- read.csv(file=file.path("../level", level_name, level_value,"Climate_Plot_data_for_level.csv"))

MAT <- Climate_Plot_data_for_level$MAT
DD5 <- Climate_Plot_data_for_level$DD5
EMT <- Climate_Plot_data_for_level$EMT
MAP <- Climate_Plot_data_for_level$MAP
MSP <- Climate_Plot_data_for_level$MSP
PAS <- Climate_Plot_data_for_level$PAS
CMD <- Climate_Plot_data_for_level$CMD
FFP <- Climate_Plot_data_for_level$FFP
TD <- Climate_Plot_data_for_level$TD

```

```{r}
mat <- ggplot(Climate_Plot_data_for_level, aes(MAT, "MAT")) +
  geom_boxplot(width = .1) 

dd5 <- ggplot(Climate_Plot_data_for_level, aes(DD5, "DD5")) +
  geom_boxplot(width = .1) 

emt <- ggplot(Climate_Plot_data_for_level, aes(EMT, "EMT")) +
  geom_boxplot(width = .1) 

map <- ggplot(Climate_Plot_data_for_level, aes(MAP, "MAP")) +
  geom_boxplot(width = .1) 

msp <- ggplot(Climate_Plot_data_for_level, aes(MSP, "MSP")) +
  geom_boxplot(width = .1) 

cmd <- ggplot(Climate_Plot_data_for_level, aes(CMD, "CMD")) +
  geom_boxplot(width = .1) 

pas <- ggplot(Climate_Plot_data_for_level, aes(PAS, "PAS")) +
  geom_boxplot(width = .1) 

ffp <- ggplot(Climate_Plot_data_for_level, aes(FFP, "FFP")) +
  geom_boxplot(width = .1) 

td <- ggplot(Climate_Plot_data_for_level, aes(TD, "TD")) +
  geom_boxplot(width = .1) 


```

```{r}
mat
#ggsave(file="mat.png", width=400, height=200, units="px")
ggsave(file="mat.png")
dd5
ggsave(file="dd5.png")
emt
ggsave(file="emt.png")
map
ggsave(file="map.png")
msp
ggsave(file="msp.png")
cmd
ggsave(file="cmd.png")
pas
ggsave(file="pas.png")
ffp
ggsave(file="ffp.png")
td
ggsave(file="td.png")

```


```{r, echo=FALSE}
df_temperature <- melt(data.frame(MAT, DD5, EMT))
df_precipitation <- melt(data.frame(MAP, MSP, PAS))
df_derived <- melt(data.frame(CMD, FFP, TD))
```

note: EMT and MAT have a very small range so their box plot is very small compared to DD5

```{r, echo=FALSE}
# ggplot(df_temperature, aes(x=as.factor(variable), y=value)) + 
#     coord_flip() +
#     geom_boxplot( alpha=0.2) +    # fill="slateblue"
#     xlab("Temperature") 
# 
# ggplot(df_precipitation, aes(x=as.factor(variable), y=value)) + 
#     coord_flip() +
#     geom_boxplot( alpha=0.2) +    # fill="slateblue"
#     xlab("Precipitation") 
# 
# ggplot(df_derived, aes(x=as.factor(variable), y=value)) + 
#     coord_flip() +
#     geom_boxplot( alpha=0.2) +    # fill="slateblue"
#     xlab("Derived") 
```

## Wind Rose

```{r, echo=FALSE}
# WindRose.R
plot.windrose <- function(data,
                      spd,
                      dir,
                      spdres = round((max(wind_rose_df$SlopeGradient) - min(wind_rose_df$SlopeGradient)) / 10),
                      dirres = 30,
                      spdmin = min(wind_rose_df$SlopeGradient),
                      spdmax = max(wind_rose_df$SlopeGradient),
                      spdseq = c(5,25,50,70, 100),
                      palette = "YlGnBu",
                      countmax = NA,
                      debug = 0) {


# Look to see what data was passed in to the function
  if (is.numeric(spd) & is.numeric(dir)){
    # assume that we've been given vectors of the speed and direction vectors
    data <- data.frame(spd = spd,
                       dir = dir)
    spd = "spd"
    dir = "dir"
  } else if (exists("data")){
    # Assume that we've been given a data frame, and the name of the speed 
    # and direction columns. This is the format we want for later use.    
  }  

  # Tidy up input data ----
  n.in <- NROW(data)
  dnu <- (is.na(data[[spd]]) | is.na(data[[dir]]))
  data[[spd]][dnu] <- NA
  data[[dir]][dnu] <- NA

  # figure out the wind speed bins ----
  # if (missing(spdseq)){
  #   spdseq <- seq(spdmin,spdmax,spdres)
  # } else {
  #   if (debug >0){
  #     cat("Using custom speed bins \n")
  #   }
  # }
  # get some information about the number of bins, etc.
  n.spd.seq <- length(spdseq)
  n.colors.in.range <- n.spd.seq - 1

  # create the color map
  spd.colors <- colorRampPalette(brewer.pal(min(max(3,
                                                    n.colors.in.range),
                                                min(9,
                                                    n.colors.in.range)),                                               
                                            palette))(n.colors.in.range)
# 
#   if (max(data[[spd]],na.rm = TRUE) > spdmax){    
#     spd.breaks <- c(spdseq,
#                     max(data[[spd]],na.rm = TRUE))
#     spd.labels <- c(paste(c(spdseq[1:n.spd.seq-1]),
#                           '-',
#                           c(spdseq[2:n.spd.seq])),
#                     paste(spdmax,
#                           "-",
#                           max(data[[spd]],na.rm = TRUE)))
#     spd.colors <- c(spd.colors, "grey50")
#   } else{
    spd.breaks <- spdseq
    spd.labels <- paste(c(spdseq[1:n.spd.seq-1]),
                        '-',
                        c(spdseq[2:n.spd.seq]))
    
    spd.labels[4] <- "70 +"
  # }
  data$spd.binned <- cut(x = data[[spd]],
                         breaks = spd.breaks,
                         labels = spd.labels,
                         ordered_result = TRUE)
  # clean up the data
  data. <- na.omit(data)

  # figure out the wind direction bins
  dir.breaks <- c(-dirres/2,
                  seq(dirres/2, 360-dirres/2, by = dirres),
                  360+dirres/2)  
  dir.labels <- c(paste(360-dirres/2,"-",dirres/2),
                  paste(seq(dirres/2, 360-3*dirres/2, by = dirres),
                        "-",
                        seq(3*dirres/2, 360-dirres/2, by = dirres)),
                  paste(360-dirres/2,"-",dirres/2))
  # assign each wind direction to a bin
  dir.binned <- cut(data[[dir]],
                    breaks = dir.breaks,
                    ordered_result = TRUE)
  levels(dir.binned) <- dir.labels
  data$dir.binned <- dir.binned

  # Run debug if required ----
  if (debug>0){    
    cat(dir.breaks,"\n")
    cat(dir.labels,"\n")
    cat(levels(dir.binned),"\n")       
  }  

  # deal with change in ordering introduced somewhere around version 2.2
  if(packageVersion("ggplot2") > "2.2"){    
    #cat("Hadley broke my code\n")
    data$spd.binned = with(data, factor(spd.binned, levels = rev(levels(spd.binned))))
    spd.colors = rev(spd.colors)
  }

  # create the plot ----
  p.windrose <- ggplot(data = data,
                       aes(x = dir.binned,
                           fill = spd.binned)) +
    geom_bar() + 
    scale_x_discrete(drop = FALSE,
                     labels = waiver()) +
    coord_polar(start = -((dirres/2)/360) * 2*pi) +
    scale_fill_manual(name = "Slope Gradient %", 
                      values = spd.colors,
                      drop = FALSE) +
    theme(axis.title.x = element_blank())

  # adjust axes if required
  if (!is.na(countmax)){
    p.windrose <- p.windrose +
      ylim(c(0,countmax))
  }

  # print the plot
  print(p.windrose)  

  # return the handle to the wind rose
  return(p.windrose)
}


```

```{r, echo=FALSE}
data.in <- read.csv(file = "wind_data.csv", col.names = c("date","hr","ws.80","wd.80"))
wind_rose_df <- ENV_Plot_data_for_level[c("Aspect", "SlopeGradient") ] %>% drop_na() %>% filter(SlopeGradient != 999) %>% filter(SlopeGradient > 5)


```

```{r}
p1 <- plot.windrose(spd = wind_rose_df$SlopeGradient,
                   dir = wind_rose_df$Aspect)

ggsave(file="windrose.png")


sloping_less_than_five <- length(which(ENV_Plot_data_for_level["Aspect"]<5))
sloping_999 <- length(which(ENV_Plot_data_for_level["Aspect"]==999))
sloping_na <- length(which(is.na(ENV_Plot_data_for_level["Aspect"])))

```

### Level count (slope < 5): `r sloping_less_than_five + sloping_999`
### No data count: `r sloping_na`

# Site 

### Elevation
```{r}

elevation <- ggplot(ENV_Plot_data_for_level, aes(Elevation, "Elevation")) +
  geom_violin() +
  geom_boxplot(width = .1) +
  coord_flip()

elevation
ggsave(file="elevation.png")


```
### Mesoslope
```{r}
meso <- env_summary$MesoSlopePosition$summary
meso
```
### Parent Material
Missing

### Humus
```{r}
humus <- env_summary$HumusForm$summary
humus

```
### Humus Thickness
Missing

### Texture
```{r}
mineral_summary <- fromJSON(file=file.path("../level", level_name, level_value, "summaries", "mineral", paste(str_replace_all(level_value, " ", "_"), ".JSON",  sep="")))

texture <- mineral_summary$Texture$summary
texture
```

### Depth to Restriction
```{r}
depth <- ENV_Plot_data_for_level$RootingDepth 
band_0_30 <- sum(depth >= 0 & depth < 30, na.rm=TRUE)
band_30_60 <- sum(depth >= 30  & depth < 60, na.rm=TRUE)
band_60_90 <- sum(depth >= 60 & depth < 90, na.rm=TRUE)
band_90_plus <- sum(depth >= 90, na.rm=TRUE)
no_data <- sum(is.na(depth))
 

band_0_30
band_30_60
band_60_90
band_90_plus
no_data
```
### Restricting Type

```{r}
rootRestrictingType <- env_summary$RootRestrictingType$summary
rootRestrictingType
```

### Gleying DEpth
Missing



