---
title: "MachineLearningHigherOrders"
author: "Will MacKenzie & Kiri Daust"
date: "05/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

require(tidyverse)
require(tidymodels)
require(data.table)
require(data.tree)
require(DataExplorer)
require(C50)
require(indicspecies)
require(doParallel)
require(philentropy)
require(dplyr)
source("./_functions/_TabletoTree.R")
source("./_functions/_TreetoTable.R")
source("./_functions/_VegdatSUsummary.R")
source("./_functions/_spp_importance.R")
```

Steps to build classification hierarchy

1. A machine learning model of high-level hierarchical BEC Forest units
a. Create a ML model of Forested SubOrders using BECv11 site series that meet minimum plot requirements. (going to Orders only causes issues where Pl is a dominant secondary species - many provincial units get placed into a Pinucon Order when applied only to the order level even though they have a subdominant tree species which places them in a different order)
b. Use only tree species for first round of model build for the forested Orders.
c. Predict membership of new BECv13 units and assign to orders then rebuild ML model.
d. Review any mis predicted site series for reassignment.
e. Compare similarity of tree composition within units (noise clustering) to find outliers that may represent new Orders (test by leaving out known units)
f. Create vegetation summaries of Orders and compare vegetation (all species now). Identify climatic indicator species groups.
g. Create climatic and site attributes summary of Orders 
h. Create maps of plot locations for each Order
i. Hierarchy tree graphic

2. Build Alliances. Focus should be on identifying species groups that reflect different site conditions.

a. Use some of the techniques of indicspecies package to create Alliances based on indicator group creation and analysis.
b. Try to build a machine learning model of Alliances
c. Vegetation and Environment summary of Alliances

3. Do pair-wise analysis of site series within Orders/Alliances using high constancy species to analyze site series and create Associations/SubAssociations.
a. Check for similarity between Associations of All orders
b. Build relationship graphic


4. Document hierarchy

5. Build model to assign new units and unassigned plots
Challenge here is to make a constant list of species between model and new units.
a. Predict membership of new site series (draft BECv13). Noise Clustering to test for novel units that do not fit any existing. Use machine learning to hierarchy
b. Predict Order membership of BECMaster plots that are unassigned to existing site series and add to an Order_unplaced site unit under each Order.

6. Build for non-forested units. Classes based on major site level differences rather than climate and using major species groups (e.g. Hydrophytic Carex spp )
May wish to assign a temporary notree pseudo species to all units that have no trees to help separate forested hierarchy from non-forested hierarchy (Hurdle model)

```{r import data}
### Vegetation From BECMaster cleaning script Long form Plot|Species|Cover (across all layers)
### or From Vpro export
#BGCZone <- fread(paste0(cloud_dir,"All_BGCs_Info_v12_2.csv"), data.table=FALSE)
vegDat2 <- fread("./BEC_ReportR/BECMaster_VegR_clean.csv", data.table = FALSE)
taxon.all <- fread("./BEC_ReportR/SpeciesMaster01Dec2020.csv", header = T, stringsAsFactors = F, strip.white = T) %>% filter(Codetype == "U")

###SU table
SUTab <- fread("./BEC_ReportR/ALLBECSU_2021_SU.csv")
#SUTab <- fread("./inputs/BECv13Analysis_Forest_17Sept2021_SU.csv")
SUTab$SiteUnit <-  trimws(SUTab$SiteUnit)
SS.names <- unique(SUTab$SiteUnit)

vegdat_test <- left_join(SUTab, vegDat2)
# #####list of official current and future correlated units from BECdb
# current <- c('Current', 'Future')
# ecotypes <- c("Forest", "Deciduous")
# #### cleaned list of official site series
# BECdb_SS <- fread("./inputs/BECdb_SiteUnitv12.csv") %>% filter(Status %in% current) %>% filter(ArchivedinVersion == "") %>% filter(`Forest-NonForest` %in% ecotypes) %>% 
#   select(MergedBGC_SS, SS_NoSpace, SiteUnitLongName, SiteUnitScientificName) %>% rename (SiteUnit = 1, SSName = 3, SciName = 4) %>% distinct(SiteUnit, .keep_all = TRUE)
# #### compare SUTab to BECdb.  Whan all BECdb units to have data and SUTab to include no unofficial units
# SS_missing <- full_join(SUTab, BECdb_SS) %>% filter(is.na(PlotNumber))
##Import Vpro hierarchy table widen and reformat
```


##roll up into site series summary data
```{r summarize site series, echo=FALSE}
#SUTab <- fread("./inputs/BECMster_V2020_2_SU.csv")
### Summarize by SU including mean cover and constancy percent
##roll up into site series summary data
### Filter out all species but tree species
vegSum <- VegdatSUsummary(vegDat2, SUTab)
vegSum2 <- spp_importance(vegSum) 

print(vegSum)
#vegDat_test <- vegSum %>% dplyr::filter(MeanCov > covercut) %>% dplyr::filter(Constancy > covercut) ## remove rare or very low cover species in SU
# 
# vegDat <- as.data.table(vegDat2)
# 
# vegDat[SUTab, SiteUnit := i.SiteUnit, on = "PlotNumber"]
# vegDat <- vegDat[!is.na(SiteUnit) & SiteUnit != "",]
# 
# vegDat <- unique(vegDat[!is.na(SiteUnit) & SiteUnit != "",])
# vegDat3 <- vegDat[,if(.N > 1) .SD, by = .(SiteUnit,Species)]
# vegDat3[,nPlots := length(unique(PlotNumber)), by = .(SiteUnit)]
# vegSum <- vegDat3[,.(MeanCov = sum(Cover, na.rm = TRUE)/nPlots[1], Constancy = (.N/nPlots[1])*100, nPlots = nPlots[1]), by = .(SiteUnit,Species)]
#fwrite(vegSum, './clean_tabs/BECv12SiteUnitSummaryVegData.csv')
```

```{r reduce summary for analysis, echo=FALSE}
##limit life forms to tree species
trees <- c(1,2)
constCut <- 0.1 ##remove species less than cutoff
covercut <- 0.1
treespp <- taxon.all[Lifeform %in% trees, ] %>% dplyr::select(Code)
treespp <- as.vector(treespp$Code)
vegDat_test <- vegSum[Species %in% treespp,]### include only trees for hierarchy build
vegDat_test <- vegDat_test %>% dplyr::filter(MeanCov > covercut) %>% dplyr::filter(Constancy > covercut)

tree.sum <- as.data.table(vegDat_test)#vegDat <- as_tibble(vegDat)
tree.sum$SiteUnit <- as.factor(tree.sum$SiteUnit)


#fwrite(tree.sum, './inputs/SiteUnitConiferSummary.csv')

```
##Import hierarchy matrix from 0_0_Plot_SU_Hierarchy script with original placements plus all unassigned units added to an unplaced Formation category
```{r import  hierarchy data}
##Import wide matrix as training data
#SUhier <- fread("./outputs/BECv12_Hierarchy_Matrix.csv")


###Import Vpro hierarchy and turn to widematrix
Vpro.hier <- fread("./BEC_ReportR/BECv13_ForestHierarchy_v2_26Sept2021_Hierarchy.csv")
Vpro.hier <- as.data.table(Vpro.hier)

#Vpro.hier <- fread("./inputs/BECv13Hierarchy_v1_22Sept2021_Hierarchy.csv")
SUhier <- treeToTable(Vpro.hier)
Hier.clean <- SUhier$table

```



```{r filter and prepare for analysis}

vegSum <- tree.sum

SS_good <- vegSum %>% filter(nPlots >=3) %>% filter(Constancy >= 33)  %>% distinct()  #%>% rename(SiteUnit = SiteUnit))## Select only site series will enough plots
Hier.units <- Hier.clean %>% dplyr::select(SiteUnit, Class, Order, Suborder) %>% distinct()
Hier.data <- left_join(Hier.units, SS_good) %>% filter(!is.na(nPlots)) %>% arrange(Species) %>% distinct()
#fwrite(Hier.data, './inputs/SiteUnitForested_w_HierarchyUnits.csv')

#print(SS_good)   # SiteUnit, Species, MeanCov, Constancy, nPlots
print(Hier.data)  # SiteUnit, Species, MeanCov, Constancy, nPlots, Class, Order, Suborder, MeanCov, Constancy

```

```{r some hierarchy stats}
classes <- unique(Hier.data$Class)
orders <- unique(Hier.data$Order)
suborders <- unique(Hier.data$Suborder)
suborders
### Choose hierarchical level for analysis

class.dat <-
  Hier.data %>% dplyr::select(SiteUnit, Suborder, Species, MeanCov) %>% 
  pivot_wider(id_cols = c(SiteUnit, Suborder),
    names_from = Species,
    values_from = MeanCov) %>% 
  mutate(Suborder = ifelse(is.na(Suborder) | Suborder == "", "unplaced", Suborder)) %>% filter(!SiteUnit == "") %>%  mutate_if(is.character, as.factor) %>% 
   replace(is.na(.),0) %>% distinct() %>% droplevels()


print(class.dat) # SiteUnit, Suborder, 45 x Species


#DataExplorer::create_report(class.dat)
```
Data pre-processing includes the following steps:  



## ---- Done ---- ##


```{r prep data, include = TRUE, echo = FALSE}

classID <- class.dat %>% dplyr::select(SiteUnit, Suborder)
#class.dat2 <- class.dat %>% select(-SiteUnit)
BEC_good <- class.dat %>% filter(!Suborder == "unplaced") %>% arrange(SiteUnit)
BEC_good$SiteUnit <- BEC_good$SiteUnit %>% as.factor
BEC_new <- class.dat %>% filter(Suborder == "unplaced") %>% arrange(SiteUnit)
SU_names <- as.data.frame(BEC_good$SiteUnit) %>%  distinct() %>% rowid_to_column('.row') %>% dplyr::rename("SiteUnit" = 2)

BEC_recipe <-
    recipe(Suborder ~ ., data = BEC_good) %>%
     update_role(SiteUnit, new_role = "id variable") %>% 
  step_novel(SiteUnit) %>% 
    prep() 
    summary(BEC_recipe)
    
BEC_fmodel <- rand_forest(mtry = 5, min_n = 2, trees = 501) %>%
  set_mode("classification") %>%
  set_engine("ranger", importance = "impurity") #or "permutations

# note in RF as a tree based model it is not required to scale and normalize covariates and may have negative influence on the model performance  

```

## -------- Don't need past this ----------- 


```{r build initial model of suborders, include = FALSE}

# 2: set up cross validation for parameter tuning data sets # note vc is default to 10 fold
BEC_workflow <- workflow() %>%
  add_model(BEC_fmodel) %>% 
    add_recipe(BEC_recipe,blueprint = hardhat::default_recipe_blueprint(allow_novel_levels = TRUE))

BEC_ranger_model <- fit(BEC_workflow, BEC_good)
BEC_ranger_model$fit

save(BEC_ranger_model, file = "./rFmodels/BECv12_Suborders_rFmodel.Rdata")

BEC.pred <- predict(BEC_ranger_model, BEC_good) %>% bind_cols(BEC_good %>% dplyr::select(SiteUnit, Suborder))  # %>% metrics(truth = Suborder, estimate = .pred_class)


BEC.pred.list <- BEC.pred$SiteUnit %>% as.character
BEC.missed <- BEC.pred  %>%    mutate(Compare = ifelse(.pred_class == Suborder, "Same", "Diff")) %>% filter(Compare == "Diff")
fwrite(BEC.missed, "./outputs/MidplacedSuborders.csv")
BEC.mis.list <- BEC.missed$SiteUnit %>% as.character
SS_misID_SU <- SUTab[SUTab$SiteUnit %in% BEC.mis.list,]
#fwrite(SS_misID_SU, "./outputs/WrongOrderPredicted_SU.csv")
```


```{r update historic hierarchy and then resubmit to create new model}
##convert matrix to tree, add in new units
#Hier.update <- fread("./clean_tabs/BEC13_HierarchyMatrixModelled_v1.csv")
Hier.update <- Hier.clean
levelNames <- c("Formation", "Class", "Order", "Suborder", "Alliance", "Suball", "Assoc", "Subass", "Facies", "Working", "SiteUnit")
testReverse <- tableToTree(hierWide = copy(Hier.update),levelNames) ## convert matrix to tree

newBEC <- BEC.pred
newBEC2 <- newBEC %>% dplyr::rename(Name = .pred_class)
pred.ID <- newBEC2 %>% select(Name) %>% distinct() %>% left_join(testReverse) %>% select(Name, ID) ## Parent Code for new predictions
newBEC3 <- left_join(newBEC2, pred.ID, by = "Name") %>% select(-Name, -Suborder) %>% dplyr::rename(Parentnew = ID, Name = SiteUnit)

testReverse2 <- left_join(testReverse, newBEC3) %>% dplyr::mutate(Parent, ifelse(!is.na(Parentnew), Parentnew, Parent)) %>% 
            select(-Parent, -Parentnew) %>% dplyr::rename (Parent = 4) %>% select(ID, Name, Parent, Level)
#testReverse2$Parent <- ifelse(testReverse2$Parent == 1, "", testReverse2$Parent) %>% as.integer
##remove old units from hierarchy.
SS.v13 <- fread( "./clean_tabs/BECv13_Forest_SiteSeries.csv",  header = T, stringsAsFactors = F, sep = "") %>% dplyr::rename(Name = SiteUnit)
SS.v13$goodv13 <- "good"
testReverse3 <- left_join(testReverse2, SS.v13) 
testReverse3 <- testReverse3 %>%  mutate(Name = ifelse(!goodv13 %in% "good" & Level == 11, NA, Name)) %>% select(-goodv13) %>% na.omit()

testReverse3$Parent <- ifelse(testReverse3$Parent == 1, "", testReverse3$Parent) %>% as.integer
###write out to Vpro format to review
fwrite(testReverse3, "./outputs/UpdatedVPROHierarchyv12_updated.csv")

SUhier2 <- treeToTable(testReverse2)
Hier.clean2 <- SUhier2$table

```

```{r build hierarchy data}
Hier.units <- Hier.clean2 %>% dplyr::select(SiteUnit, Class, Order, Suborder) %>% distinct()
###new SU table

Hier.data2 <- left_join(Hier.units, SS_good) %>% filter(!is.na(nPlots)) %>% arrange(Species) %>% distinct()

class.dat2 <-
  Hier.data2  %>% dplyr::select(SiteUnit, Suborder, Species, MeanCov) %>% 
  pivot_wider(id_cols = c(SiteUnit, Suborder),
    names_from = Species,
    values_from = MeanCov) %>% 
  mutate(Suborder = ifelse(is.na(Suborder) | Suborder == "", "unplaced", Suborder)) %>% filter(!SiteUnit == "") %>%  mutate_if(is.character, as.factor) %>% 
   replace(is.na(.),0) %>% distinct() %>% droplevels()
```

```{r build new model}
classID <- class.dat2 %>% dplyr::select(SiteUnit, Suborder)
#class.dat2 <- class.dat %>% select(-SiteUnit)
BEC_good2 <- class.dat2 %>% filter(!is.na(Suborder) & !Suborder %in% "unplaced") %>% arrange(SiteUnit)
BEC_good2$SiteUnit <- BEC_good2$SiteUnit %>% as.factor
SU_names <- as.data.frame(BEC_good2$SiteUnit) %>%  distinct() %>% rowid_to_column('.row') %>% dplyr::rename("SiteUnit" = 2)

BEC_recipe <-
    recipe(Suborder ~ ., data = BEC_good2) %>%
     update_role(SiteUnit, new_role = "id variable") %>% 
  step_novel(SiteUnit) %>% 
    prep() 
    summary(BEC_recipe)
    
BEC_fmodel <- rand_forest(mtry = 5, min_n = 2, trees = 501) %>%
  set_mode("classification") %>%
  set_engine("ranger", importance = "impurity") #or "permutations
```

```{r build  second model of suborders, include = FALSE}

# 2: set up cross validation for parameter tuning data sets # note vc is default to 10 fold
BEC_workflow <- workflow() %>%
  add_model(BEC_fmodel) %>% 
    add_recipe(BEC_recipe,blueprint = hardhat::default_recipe_blueprint(allow_novel_levels = TRUE))

BEC_ranger_model <- fit(BEC_workflow, BEC_good2)
BEC_ranger_model$fit

save(BEC_ranger_model, file = "./rFmodels/BECv12_Suborders_rFmodel_Updated.Rdata")

BEC.missed2 <- predict(BEC_ranger_model, BEC_good2) %>% bind_cols(BEC_good2 %>% dplyr::select(SiteUnit, Suborder)) %>% 
  mutate(Compare = ifelse(.pred_class == Suborder, "Same", "Diff")) %>% filter(Compare == "Diff")
BEC.mis.list2 <- BEC.missed2$SiteUnit %>% as.character

SS_misID_SU <- SUTab[SUTab$SiteUnit %in% BEC.mis.list2,]
fwrite(SS_misID_SU, "./outputs/WrongOrderPredicted_SU.csv")
```

